A Topic Model of Climate Change Literature

### 2017-05-24 main.tex
shared

\documentclass{article}
\usepackage[a4paper, total={7in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/hot_topics}
    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled [Example figure]}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{plots/ipcc_topics}
    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
\end{figure}

@@

\section*{Results}
\begin{itemize}
	\item The biggest topics are x and y
	\item These topics have grown, these have decreased
    \item X keywords fit into Y topics like so...
    \item Finding similar documents works across topics, rather than just by keywords, so better.
    \item Similar documents more or less likely to be across disciplinary boundaries ??
    \item Model selection validated by these measurements.
\end{itemize}

\section{*Conclusion}
\begin{itemize}
	\item A very simple topic model provides an overview of the whole landscape.
    \item This allows researchers / assessment makers to identify areas that have grown recently
    \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
    \item Next steps for research: using topic models to assess the assessment process: find gaps etc.
\end{itemize}

\begin{figure}
	%\includegraphics{}
    \caption{Topic structure of climate change literature [network plot]}
\end{figure}

>>>>

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/hot_topics_65}
    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled [Example figure]}
    \label{topic_growth}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{plots/ipcc_topics}
    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
    \label{IPCC}
\end{figure}

@@

\section*{Results}
\subsection*{Literature Description}
\begin{itemize}
	\item Some big/interesting topics are x and y
	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
    \item
\end{itemize}

\subsection*{Information Retrieval Implications}
\begin{itemize}
    \item X keywords fit into Y topics like so...
    \item Finding similar documents, how does this work with topics as opposed to keywords?
    \item Similar documents more or less likely to be across disciplinary boundaries ??
\end{itemize}

\section*{Conclusion}
\begin{itemize}
	\item A very simple topic model provides an overview of the whole landscape.
    \item This allows researchers / assessment makers to identify areas that have grown recently
    \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
    \item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
\end{itemize}

\begin{figure}
	\includegraphics[width=\linewidth]{plots/snip}
    \caption{Topic structure of climate change literature [network plot]}
    \label{network}
\end{figure}
